\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
Reworking open questions

\subsection{Open questions}
There are many studies about the influence of games in everyday life. Some scientists (see Jane McGonigal) are trying to use games to let people learn to get the most out of their lifes. Her experiments show that habits changed during playing a game with real world content like a global lack of oil are kept by most of the players even after ending the game. These experiments were made with small groups of 500 to 1700 people as a sort of proof of concept. No one knows what impact it may have when millions of people are achieving a healthier life through various gaming strategies and what comes out of the motivation they put into it. So many questions in the area of wide field gamification are still not answerable.

>>>>

\subsection{Open questions}
The game designer and scientist Jane McGonigal, once suffering from depression herself, investigates in several research projects and studies on how gamification can improve people's life and happiness \footnote{\url{http://janemcgonigal.com/learn-me/}}. For this purpose she once created a game SuperBetter to treat herself, leading to the founding of her company SuperBetter Labs. Her experiments show that habits learned during playing a game with real world content can influence people‘s behaviour even after the game already ended. The game \emph{World without Oil} \footnote{\url{http://worldwithoutoil.org/metaabout.htm}} is an alternate reality game to call attention to a possible future oil shortage. People playing this game showed to be more sensitive for sustainable oil usage afterwards. The open question we want to answer is whether gamification can have a similar impact on the long-term attitude of people towards living a healthy life. We want to find out which factors can lead to a success or a failure of this system and how different societies need different motivations factors. \\

Another open question we want to answer is if and how different isolated systems can be interconnected in a useful way, and whether we can infer a general approach for such a task. One important point of the interconnected data mining is to not sacrify security and privacy, while still keeping the possibility to do useful evaluations and create meaningful statistics. There are several algorithms that can be used to do privacy-preserving data mining like Partitioning, Randomization, Group Based Anonymization or special algorithms for Distributed privacy-preserving data mining \citep{agrawal2000}. We need to reasearch which algorithms are most suitable for our needs.
